Ice sheet mass flows

### 2024-06-05 sankey.tex
Remove unused commented code
Red outline for processes that change plan-view boundary

    \sankeyset{
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/33,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-water-horiz/.style={fill/.style={fill=none, right color=ice, left color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-air-horiz/.style={fill/.style={fill=none, left color=ice, right color=air},},
      water-to-air-horiz/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

      %% \sankeynode{name=fMGa, quantity=\qq{fMG},
      %%   at={[xshift=\xoff,yshift=8mm]fSUa.left}, anchor=right, angle=0}
      %% \sankeyoutin{fMG}{fMGa}
      %% \sankeyadvance[ice-to-air]{fSUa}{10mm}; \sankeyend[air]{fSUa}

@@

      %% \sankeyoutin{fMG}{fMGa}

      \sankeyadvance{fFRa}{10mm}; \sankeyend{fFRa}
      \sankeyadvance[ice-to-water]{fGZa}{10mm}; \sankeyend[water]{fGZa}
      \sankeyadvance{fD}{10mm}; \sankeyend{fD}

@@

      %% \foreach \mag in {SF,f0,RFZ-in,f6,fRU,fSUBa,fD,fGZa,fFRa,fSUa2,fEVa} {
      %%   \node at (\mag.center) {\qq{\mag}};
      %% }

      %% \ifthenelse{\Q{MG} < \Q{ML}} {
      %%   \node at (fML.center) {\qq{fML}};
      %% } {
      %%   \node at (fMGa.center) {\qq{fMGa}};
      %% }

>>>>

    \sankeyset{
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/33,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-water-horiz/.style={fill/.style={fill=none, right color=ice, left color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-air-horiz/.style={fill/.style={fill=none, left color=ice, right color=air},},
      water-to-air-horiz/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

@@

      \sankeyadvance[out-red]{fFRa}{10mm}
      \sankeyend[out-red]{fFRa}
      \sankeyadvance[ice-to-water,out-red]{fGZa}{10mm}
      \sankeyend[water,out-red]{fGZa}
      \sankeyadvance{fD}{10mm}
      \sankeyend{fD}

@@
